\HAWAbstractPage
  {
    Clustering, Cluster Analyse, 
    Dokument Clustering, Vector Space Model,
    Partitionelles Clustering,
    Hierarchisches Clustering,
    Probabilistic Topic Modeling, 
    Text Zusammenfassung,
    Text Mining, Data Mining,
    Machinelles Lernen, Unüberwachtes Lernen, 
    Information Retrieval
  }
  { 
    Für eine Maschine ist es schwer, ohne die Supervision eines menschlichen Expertens Text zu interpretieren. Techniken des Text Minings und Clustern als Ansatz von unsupervisierten Lernen, um Text aus Zeitungen in Kategorien und zu Ereignissen in der realen Welt zu gruppieren, ist im Mittelpunkt dieser Arbeit. Zusätzlich wurde ein funktionierendes Datenverarbeitungssystem, zum Herunterladen und Verarbeiten von Zeitungsartikeln, entwickelt, um Clustering Algorithmen eine Grundlage zu geben. Die präsentierten Selektionsstrategien und Clustering Algorithmen haben ähnliche Effekte auf die Resultate.
  }
  { 
    Clustering, Cluster Analysis, 
    Document Clustering, Vector Space Model,
    Partitional Clustering,
    Hierarchical Clustering,
    Probabilistic Topic Modeling,
    Summarization,
    Text Mining, Data Mining,
    Machine Learning, Unsupervised Learning, 
    Information Retrieval
  }
  {
    Interpreting and summarizing textual content without the supervision of human experts is an exploratory process involving NP-hard algorithms. Using techniques of text mining and document clustering as an approach of unsupervised machine learning, grouping textual content of online newspaper articles into coherent categories and real world events is subject of this thesis. Additionally, building a functioning data pipeline for scraping and preprocessing newspaper articles, feeding clustering algorithms, shows promising results. In short, the presented feature selection and clustering strategies yield similar effects.
  }



